### 2021-03-26 chapters/sections/11-technological_integration.tex
finished

In this section an integration architecture is presented for integration of the IMP system presented in section \ref{imp} into the existing OZG system architecture presented in section \ref{ozg}.

\subsection{Integration Requirements}
Purpose of the integration architecture is to enable the existing OZG system to access IMP services according to the previously described IMP solution. It therefore has to enable the creation of an onboarding relationship template, the processing of onboarding relationship requests and the processing of established relationships through creation of user profiles. \\ 
In addition to that, it has to enable the definition and utilization of message types listed in the IMP solution. This are messages for attribute changes, communication and authentication. As the approach of the IMP solution is the mapping between user profiles and IMP relationships, the integration architecture has to enable an effortless translation between the two entities. OZG system architecture and IMP systems use different data models, especially in regard to personal information. The integration architecture therefore has to translate between them. As the IMP connector is not capable of sending asynchronous notifications, the integration architecture has to add this functionality. Depending on the use case of Service Providers, multiple types of relationships or in this case multiple types of user profiles might be necessary. The integration architecture has to enable each type of relationship and user profile to be processed separately, as they might have different processing legitimization. OZG and the presented IMP solution are only one example of a system architecture and IMP use case. The integration architecture should be able to be used in various different scenarios. It therefore has to be configurable and expandable in order to meet new requirements.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
    \caption{Insertion of Integration Systems into OZG System Architecture}
    \label{integration1:integration_overview}
\end{figure}

The IMP solution described in the previous section requires the administration portal to access IMP services. As shown in figure \ref{integration1:integration_overview}, an IMP connector and a messaging system are added to the administration portal for integration. Using the messaging system, existing systems of the administration portal and IMP connector can access each others services. IMP server and IMP client of the IMP system as described in section \ref{section:imp_system} are also displayed in figure \ref{integration1:integration_overview}.

In order for the integration not to be invasive, only the web server and the service facade of the administration portal are connected to the messaging system. All other existing system components remain untouched. Through the service facade, the messaging system can integrate services of all connected service components.

\subsection{Onboarding Sequence}
This section describes the sequence of an application process as visualized in figure \ref{integration1:onboarding_overview}.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
    \caption{Onboarding Overview}
    \label{integration1:onboarding_overview}
\end{figure}

The user should be able to create a new user profile for the OZG system through an existing IMP identity.

@@

A messaging approach is used for the technological integration. As described in section \ref{messaging}, messaging enables the systems to access each others services in a decoupled way. This is a useful feature as the integration architecture should be reusable for different system architectures. The messaging patterns described in section \ref{messaging} also enable the integration architecture to be configured according to changes in the operation of the existing systems. The asynchronous nature of messaging systems translates well to the asynchronous and message based operation of the IMP system and IMP solution.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/3. Messaging Integration.pdf}
    \caption{Messaging Integration}
    \label{integration1:messaging_integration}
\end{figure}

The main task of the integration system is to translate between the domain of the existing system architecture and the domain of the IMP system. None of the existing systems can process IMP relationships but they can process user profiles and vice versa.

As shown in figure \ref{integration1:messaging_integration}, on the side of the administration portal, messaging adapters provide an API to the existing systems that is providing access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system. The adapters communicate with the messaging system through channels. Messages placed on each channel can be simultaneously accessed by multiple systems. Using these channels, message adapters can send requests and replies, and receive replies, notifications and requests

@@

Messaging adapters do not communicate directly through channels, but with messaging modules. Messaging modules consist of messaging patterns which are able to modify, delete and route messages. Purpose of the modules is to translate messages sent by messaging adapters of either Service Provider or connector to be understood by the respective recipient. Each module is assigned to an individual integration task. By adding or removing modules, integration capabilities of the messaging system can be suited to the system architecture of the Service Provider. Modules can be designed to provide services to messaging adapters or other modules. Designing modules specifically for the usage by other modules helps in distributing integration responsibilities and avoiding a single monolithic integration component.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
    \caption{Messaging System Overview}
    \label{integration1:messaging_system_overview}
\end{figure}

Figure \ref{integration1:messaging_system_overview} gives an overview of the messaging system which will be discussed in detail in the following sections. The figure contains all channels and messaging modules along with their connectivity.

@@

Three messaging modules exist on the "Relationship to Identity Integration Layer", which directly access services of the connector. The onboarding template module provides the feature of creating relationship templates for onboarding. The onboarding request module, provides the feature of processing and responding to relationship requests. And the onboarding relationship module provides the feature of processing established relationships by creating a new user profile. The relationship mapping module has the purpose of combining "Relationship to Identity Integration Layer" and "Communication Integration Layer" by enabling the messaging system to map relationships to the corresponding entity of the Service Provider. In this case, the module maps IDs of relationships to IDs of user profiles. Each relationship has a one-to-one relationship to a user profile.

The "Communication Integration Layer" consists of modules, that enable the existing systems to exchange structured data with the IMP client. Purpose of the modules is to translate between the data models of the Service Provider and the IMP system. Most importantly in this case, none of the existing systems is able to understand relationships or relationship IDs. Therefore, the message mapping module has the purpose of translating all incoming relationship IDs to user profile IDs with the help of the previously mentioned relationship mapping module on the underlying layer. \\
Three message modules are included. Each of them has the purpose of identifying messages of a certain type and separate them onto individual channels. This enables the construction of various modules processing the same message types in different ways. However, in this case, each message type has only a single module processing it. Modules, that eventually process the messages, have the purpose of translating the message content between the data models of Service Provider and IMP system. For example the mail module consumes messages which contain a mail received by a user profile. It is very likely that the inbox of the user profile and the inbox of the IMP system process mails with different data representation and data types. The mail module therefore has to convert the format of the mail content.

@@

In this section each messaging module mentioned in the overview of the message architecture is described.

@@

To present an onboarding relationship template to the user, the web server first has to retrieve it from the messaging system. For this purpose, an "Onboarding Template Module" is added to the messaging system. Using the API of a messaging adapter provided in addition to the module, the web server can request the creation of new onboarding templates. Optionally, the web server can pass additional attributes which should be stored in the metadata section of the template. In this case, the web server will need to notify the user about the successful creation of his user profile. The web server therefore adds the user's current session ID as metadata to the template.

The messaging adapter is aware of the existence of two channels: the "Onboarding Template Request" channel, where it publishes its requests, and the "Onboarding Template Response" channel, where it listens for responses. In order for the adapter to correlate request and reply messages, it creates a message that contains a request ID additionally to the Template Metadata. This ID is expected to be included in the response message. The message ID is a unique identifier and is part of every message. The module consumes messages from the "Onboarding Template Request" channel. On each channel connected to a messaging adapter, message translators are attached. These translators have the purpose of providing a canonical data model within the module by translating messages on the data representation, data types and data structures layer. It might happen, that in the future one of the adapters switches from using for example an XML instead of a JSON data representation. Using message translators on each side enables to adapt to these changes by only appropriately configuring the translator while leaving the rest of the module untouched.

In between the message translators the module copies a configuration object stored in a template configuration database into the message and combines it with the template metadata attribute. This configuration contains information on how the relationship templates of type onboarding are supposed to look like. It specifies the title of the template, which attributes will be requested from the user, the reason why the attributes are requested and more. If the content of relationship templates should be changed in the future, depending on the severity of the changes, either a new template module can be created or the configuration stored in the database can be edited. Purpose of the relationship template is to eventually create a new user profile based on the attributes shared by the IMP identity. \\ 
Therefore all attributes that are required to create a user profile have to be requested by the template. In the template, attributes have to be requested according to the data model of the IMP system in order for the IMP client to understand them. When receiving a response later, a module will translate the attributes back to the OZG data model.

After enriching the message with the template configuration, the message is published on the "Template Request" channel. The messaging adapter of the connector consumes the message and issues the appropriate REST request to the connector. After receiving a response from the connector it publishes the resulting template along with the request ID on the "Template Response Channel". As this channel can contain responses to requests from any amount of modules concerning different template types, the "Onboarding Template Module" filters all incoming messages which contain templates of the type "onboarding" and publishes them on the "Onboarding Template Response" channel.

@@

Eventually, the user scans the QR code, fills in the attributes and submits a relationship request. The request is received by the connector, then forwarded to the messaging adapter and published on the "Relationship Request" channel. The message contains a relationship ID created by the IMP server to uniquely identify the request and the resulting relationship. It also contains the request content with attributes shared by the user and the template the request originated from. Messages on the "Relationship Request" channel are consumed by the "Onboarding Request Module". As in the previous example, message translators are included to construct a canonical data model for the module. A message filter only lets messages through that contain templates of type onboarding. The message translator connected to the "Onboarding Request" channel translates attributes shared by the user from the IMP data model to the OZG data model.

@@

If the user did not retract their relationship request before the OZG system accepted it, the relationship is established and the connector receives a corresponding notification that the messaging adapter publishes on the "Relationship Established" channel. The message contains the ID of the established relationship along with all attributes shared by the user. The "Onboarding Relationship" module consumes messages from the channel and is responsible for maintaining the state of onboarding relationships. In this case, the module only processes the establishing of relationships, it could however be expanded to also process terminations of relationships.

@@

To create a user profile, a messaging adapter attached to the service facade of the administration portal consumes messages from the "Create User Profile Request" channel and issues the corresponding requests to the service facade for creating a new user profile based on the attributes stored in the relationship content. After successful creation of the user profile the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created user profile ID.

@@

Using messaging for this form of database access enables modules to stay unaware of the complexities of the underlying data storage mechanisms. An alternative would be for modules to use the database as a shared database.

@@

Using the previously defined "Relationship Mapping" module, the "Message Mapping" module has the purpose of translating the relationship ID of all inbound messages to the corresponding user profile ID and translating the user profile ID of all outbound messages to the corresponding relationship ID. As a result of that, on the left side of the figure \ref{integration1:message_mapping_module}, messages coming from or going to the existing system architecture contain identification of the known user profile entity instead of the unknown relationship entity. On the right side, messages coming from or going to the IMP system contain identification of the known relationship instead of the unknown user profile.

Incoming messages on the "Message Inbound" channel are consumed by the module and translated by a message translator to a canonical data model. In order for the module to identify a response after publishing the message on the "Relationship Mapping Request" channel, a Content Enricher adds a unique request ID to the message and stores the ID in a database. Only messages on the "Relationship Mapping Response" channel containing a request ID stored in the database are let through by the request ID message filter. As the following systems will process the inserted user profile ID instead of the relationship ID, a content filter removes relationship IDs from the message before publishing it on the "Message Inbound Mapping" channel.

@@

For the messaging system to process messages being exchanged as part of relationships, message modules can be added. Their purpose is to map messages of certain types from the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them. They also map messages of the individual message type channels to the "Message Outbound Mapping" channel to so that the connector can submit them.

In this case an "Attribute Change Message Module" is included, which processes messages related to the attribute change process. Messages exchanged through IMP relationships can have arbitrary content. However, the messages are assumed to contain a message type attribute and a message content attribute. Based on the message type attribute a message filter can let messages through that contain a message type attribute correlating to an attribute change process. Based on the type of a message, a content based message router then copies each message to a datatype channel. In this example, messages of type attribute change request and attribute change established are distinguished. Corresponding to that, two data type channels exist. As the type of a message can be inferred from the channel it is placed on, content filters can remove the message type attributes.

Outbound messages related to the attribute change process are consumed in data type channels. In this case it is only one "Attribute Change Response" channel. A Content Enricher adds a message type attribute correlating to the channel the message was placed on. This is required in order for the IMP client to properly interpret the message. After that the message is published on the "Message Outbound Mapping" channel.

@@

To process incoming attribute change requests for profiles, a "User Profile Attribute Change Request" module is included which consumes messages from the "Attribute Change Request" channel. Messages arriving on the "Attribute Change Request" channel were mapped from a relationship ID to a user profile ID in an earlier integration step. Depending on the use case of the Service Provider, not all attribute change requests for user profiles should be processed in the same way. Therefore, message filters are inserted which are able to distinguish possible "types" of user profiles based on the user profile ID. It would also be possible to include an additional module that is able to request user profile type information from the existing systems, separating messages on the "Attribute Change Request" channel appropriately. For example, user profiles for businesses could exist, where processing of attribute change requests requires a more thorough and manual verification by employees.

@@

Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the Service Provider. Therefore the SP is expected to include a "Profile Attribute Change Processor" module, which decides to approve or reject the request based on the user profile ID and the shared attributes. The response is published to the "Attribute Change Response" channel and contains the user profile ID additionally to the response.

@@

If the user did not cancel the attribute change request before the OZG system accepted it, the attribute change is established. The connector is notified through a message, which eventually is processed by the "User Profile Attribute Change Message" module described earlier and published on the "Attribute Change Established" channel.

The "User Profile Attribute Sync" module consumes messages from the "Attribute Change Established" channel. Similar to the "User Profile Attribute Change Request" module, a message filter is inserted for distinguishing possible user profile types based on the user profile ID. A message translator is inserted to translate the message content to the OZG data model. This concerns especially the attributes shared as part of the attribute change established message.

@@

Before publishing messages on the "Message Outbound Mapping" channel, a Content Enricher adds the implicit message type of the channel as attribute in order for the IMP client to understand it.

@@

If the user creates a user profile using their IMP identity, it is possible to replace password authentication with an authentication through the IMP client. It is also possible to use the IMP client for two factor authentication.

In order to send and receive messages related to authentication, similar to previous message modules, an "Authentication Message" module is included which maps incoming messages on the "Message Inbound Mapping" channel to the "Authentication Response" channel and outgoing messages from the "Authentication Request" channel to the "Message Outbound" channel.

@@

When the users visit the web page of the administration portal to apply for an administrative service, they will have to login. To utilize the IMP client for authentication, the web server can use a channel adapter to publish an authentication request concerning a user profile ID and a certain session ID. The adapter publishes a message on the "Authenticate" channel which contains the profile ID and a request content. Next to the session ID, the request content may also include information for presentation to the user like the current time or the IP address of the browser. Similar to previous modules, a message translator is inserted to translate the message to a canonical data model and publish it on the "Authentication Request Message" channel.

Eventually, the IMP client sends a response as a message, which the "Authentication Message" module publishes on the "Authentication Response" channel. Similar to previous modules the Service Provider can use a message filter to process user profile types differently. After translating the message to the OZG data model, it is published on the "Authenticate Profile Response" channel. The channel adapter of the web server receives the message and based on the session ID contained in the response content can authenticate the browser session.

@@

The messaging system and the modular approach make integration architecture expandable and configurable for new integration scenarios.
Message mapping module and relationship mapping module enable the translation between user profile and relationship.
Onboarding template, onboarding request and onboarding relationship module enable the definition and utilization of one or more relationship types.
Message modules enable the definition of message types.
Message processing modules enable the translation between data models.
Messaging system enables asynchronous, event based and direct communication between user and Service Provider.
Assigning special modules to each type of relationship and message type enables the separation of processing depending on differences in processing legitimization.

>>>>

In this section, an integration architecture is presented for integration of the IMP system presented in section \ref{imp} into the existing OZG system architecture presented in section \ref{ozg}.

\subsection{Integration Requirements}
Purpose of the integration architecture is to enable the existing OZG system to access IMP services according to the previously described IMP solution. It therefore has to enable the creation of an onboarding relationship template, the processing of onboarding relationship requests, and the processing of established relationships through the creation of user profiles. \\ 
In addition to that, it has to enable the definition and utilization of message types listed in the IMP solution. This are messages for attribute change, communication and authentication. As the approach of the IMP solution is the mapping between user profiles and IMP relationships, the integration architecture has to enable an effortless transition between the two entities. OZG system architecture and IMP systems use different data models, especially regarding personal information. The integration architecture therefore has to translate between them. As the IMP connector is not capable of sending asynchronous notifications, the integration architecture has to add this functionality. Depending on the use case of Service Providers, multiple types of relationships or in this case multiple types of user profiles might be necessary. The integration architecture has to enable each type of relationship and user profile to be processed separately, as they might have different processing legitimization. OZG and the presented IMP solution are only one example of a system architecture and IMP use case. The integration architecture should usable in various scenarios. It therefore has to be configurable and expandable to meet new requirements.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
    \caption{IMP Integration for OZG System Architecture}
    \label{integration1:integration_overview}
\end{figure}

The IMP solution described in the previous section requires the administration portal to access IMP services. As shown in figure \ref{integration1:integration_overview}, an IMP connector and a messaging system are added to the administration portal for integration. Using the messaging system, the existing systems of the administration portal and IMP connector can access each others services. IMP server and IMP client of the IMP system as described in section \ref{section:imp_system} are also displayed in figure \ref{integration1:integration_overview}.

In order for the integration not to be invasive, only the web server and the service facade of the administration portal are connected to the messaging system. All other existing system components remain untouched. Through the service facade, the messaging system can integrate the services of all connected service components.

\subsection{Onboarding Process}
This section describes the process of an application for an administrative service as visualized in figure \ref{integration1:onboarding_overview}.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/5. Onboarding Overview.pdf}
    \caption{User Profile Onboarding Process}
    \label{integration1:onboarding_overview}
\end{figure}

As stated by the IMP solution, the user has to be able to create a new user profile for the OZG system through an existing IMP identity.

@@

A messaging approach is used for the technological integration. As described in section \ref{messaging}, messaging enables the systems to access each others services in a decoupled way. This is a useful feature as the integration architecture should be reusable for different system architectures. The messaging patterns described in section \ref{messaging} also enable the integration architecture to be configured according to changes in the operation of the existing systems. The asynchronous nature of messaging systems translates well to the asynchronous and message-based operation of the IMP system and IMP solution.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/3. Messaging Integration.pdf}
    \caption{Messaging System Layout}
    \label{integration1:messaging_integration}
\end{figure}

The main task of the integration system is to translate between the domain of the existing system architecture and the domain of the IMP system. None of the existing systems can process IMP relationships, but they can process user profiles and vice versa.

As shown in figure \ref{integration1:messaging_integration} on the side of the administration portal, messaging adapters provide an API to the existing systems. They give access to IMP services while hiding the technological details of the operation of the IMP system and the underlying messaging system. The adapters communicate with the messaging system through channels. Messages placed on each channel can be simultaneously accessed by multiple systems. Using these channels, message adapters can send requests and replies, and receive replies, notifications, and requests

@@

Messaging adapters do not communicate directly through channels, but with messaging modules. Messaging modules consist of messaging patterns which are able to modify, delete, and route messages. Purpose of the modules is to translate messages sent by messaging adapters of either Service Provider or connector to be understood by the respective recipient. Each module is assigned to an individual integration task. By adding or removing modules, the integration capabilities of the messaging system can be suited to the system architecture of the Service Provider. Modules can be designed to provide services to messaging adapters or other modules. Designing modules specifically for usage by other modules helps in distributing integration responsibilities and avoiding a single monolithic integration component.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 1/Technological Integration/4. Messaging Overview.pdf}
    \caption{Messaging System Detailed Layout}
    \label{integration1:messaging_system_overview}
\end{figure}

Figure \ref{integration1:messaging_system_overview} gives an overview of the messaging system, which will be discussed in detail in the following sections. The figure contains all channels and messaging modules along with their connectivity.

@@

Three messaging modules exist on the "Relationship to Identity Integration Layer", which directly access services of the connector. The onboarding template module provides the feature of creating relationship templates for onboarding. The onboarding request module provides the feature of processing and responding to relationship requests. And the onboarding relationship module provides the feature of processing established relationships by creating a new user profile. The relationship mapping module has the purpose of combining "Relationship to Identity Integration Layer" and "Communication Integration Layer" by enabling the messaging system to map relationships to the corresponding entity of the Service Provider. In this case, the module maps IDs of relationships to IDs of user profiles.

The "Communication Integration Layer" consists of modules that enable the existing systems to exchange structured data with the IMP client. Purpose of the modules is to translate between the data models of the Service Provider and the IMP system. Most importantly, in this case, none of the existing systems is able to understand relationships or relationship IDs. Therefore, the message mapping module has the purpose of translating all incoming relationship IDs to user profile IDs with the help of the previously mentioned relationship mapping module on the underlying layer. \\
Three message modules are included. Each of them has the purpose of identifying messages of a certain type and separating them into individual channels. This enables the construction of various modules processing the same message types in different ways. Modules that eventually process the messages have the purpose of translating the message content between the data models of Service Provider and IMP system. For example, the mail module consumes messages which contain a mail received by a user profile. It is very likely that the inbox of the user profile and the inbox of the IMP system process mails with different data representation and data types. The mail module therefore has to convert the format of the mail content.

@@

In this section, each messaging module mentioned in the overview of the message architecture is described.

@@

To present an onboarding relationship template to the user, the web server first has to retrieve it from the messaging system. For this purpose, an "Onboarding Template Module" is added to the messaging system. Using the API of a messaging adapter provided in addition to the module, the web server can request the creation of new onboarding templates. Optionally, the web server can pass additional attributes which should be stored in the metadata section of the template. The web server will need to notify the user about the successful creation of his user profile and therefore adds the session ID of the user as metadata to the template.

The messaging adapter is aware of the existence of two channels: the "Onboarding Template Request" channel, where it publishes its requests, and the "Onboarding Template Response" channel, where it listens for responses. In order for the adapter to correlate request and reply messages, it creates a message that contains a request ID additionally to the Template Metadata. This ID is expected to be included in the response message. The message ID is a unique identifier and is part of every message. The module consumes messages from the "Onboarding Template Request" channel. On each channel connected to a messaging adapter, message translators are attached. These translators have the purpose of providing a canonical data model within the module by translating messages on the data representation, data type, and data structure layers. It might happen that in the future one of the adapters switches from using, for example, an XML instead of a JSON data representation. Using message translators on each side enables to adapt to these changes by only configuring the translator while leaving the rest of the module untouched.

In between the message translators, the module copies a configuration object stored in a template configuration database into the message and combines it with the template metadata attribute. This configuration contains information on how the relationship templates with type onboarding are supposed to look like. It specifies the title of the template, which attributes will be requested from the user, the reason the attributes are requested, and more. If the content of relationship templates should be changed in the future, depending on the severity of the changes, either a new template module can be created or the configuration stored in the database can be edited. Purpose of the relationship template is to eventually create a new user profile based on the attributes shared by the IMP identity. \\ 
Therefore, all attributes that are required to create a user profile have to be requested by the template. In the template, attributes have to be requested according to the data model of the IMP system in order for the IMP client to understand them. When receiving a response later, a module will translate the attributes back to the OZG data model.

After enriching the message with the template configuration, the message is published on the "Template Request" channel. The messaging adapter of the connector consumes the message and issues the appropriate REST request to the connector. After receiving a response from the connector, it publishes the resulting template along with the request ID on the "Template Response Channel". As this channel can contain responses to requests from any amount of modules concerning different template types, the "Onboarding Template Module" filters all incoming messages which contain templates of the type "onboarding" and publishes them on the "Onboarding Template Response" channel.

@@

Eventually, the user scans the QR code, fills in the attributes, and submits a relationship request. The request is received by the connector, then forwarded to the messaging adapter and published on the "Relationship Request" channel. The message contains a relationship ID created by the IMP server to uniquely identify the request and the resulting relationship. It also contains the request content with attributes shared by the user and the template the request originated from. Messages on the "Relationship Request" channel are consumed by the "Onboarding Request Module". As in the previous example, message translators are included to construct a canonical data model for the module. A message filter only lets messages through that contain templates of type onboarding. The message translator connected to the "Onboarding Request" channel translates the attributes shared by the user from the IMP data model to the OZG data model.

@@

If the user did not retract their relationship request before the OZG system accepted it, the relationship is established and the connector receives a corresponding notification that the messaging adapter publishes on the "Relationship Established" channel. The message contains the ID of the established relationship along with all attributes shared by the user. The "Onboarding Relationship" module consumes messages from the channel and is responsible for maintaining the state of onboarding relationships. In this case, the module only processes the establishing of relationships, it could however be expanded to process the termination of relationships.

@@

To create a user profile, a messaging adapter attached to the service facade of the administration portal consumes messages from the "Create User Profile Request" channel and issues the corresponding requests to the service facade for creating a new user profile based on the attributes stored in the relationship content. After successful creation of the user profile, the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created user profile ID.

@@

Using messaging for this form of database access enables modules to stay unaware of the complexity of the underlying data storage mechanisms. An alternative would be for modules to use the database as a shared database.

@@

Using the previously defined "Relationship Mapping" module, the "Message Mapping" module has the purpose of translating the relationship ID of all inbound messages to the corresponding user profile ID and translating the user profile ID of all outbound messages to the corresponding relationship ID. As a result of that, on the left side of the figure \ref{integration1:message_mapping_module}, messages coming from or going to the existing system architecture contain the identification of the known user profile entity instead of the unknown relationship entity. On the right side, messages coming from or going to the IMP system contain the identification of the known relationship instead of the unknown user profile.

Incoming messages on the "Message Inbound" channel are consumed by the module and translated by a message translator to a canonical data model. In order for the module to identify a response after publishing the message on the "Relationship Mapping Request" channel, a Content Enricher adds a unique request ID to the message and stores the ID in a database. Only messages on the "Relationship Mapping Response" channel containing a request ID stored in the database are let through by the request ID message filter. As the following systems will process the inserted user profile ID instead of the relationship ID, a content filter removes the relationship IDs from the message before publishing it to the "Message Inbound Mapping" channel.

@@

For the messaging system, to process messages being exchanged as part of relationships, message modules can be added. Their purpose is to map messages of certain types from the "Message Inbound Mapping" channel to individual message type channels so that the modules can process them. They also map messages from the individual message type channels to the "Message Outbound Mapping" channel so that the connector can submit them.

In this case an "Attribute Change Message Module" is included, which processes messages related to the attribute change process. Messages exchanged through IMP relationships can have arbitrary content. However, the messages are assumed to contain a message type attribute and a message content attribute. Based on the message type attribute, a message filter can let messages through that contain a message type attribute correlating to an attribute change process. Based on the type of a message, a content-based message router then copies each message to a datatype channel. In this example, messages with the type "attribute change request" and "attribute change established" are distinguished. Corresponding to that, two data type channels exist. As the type of a message can be inferred from the channel it is placed on, content filters can remove the message type attributes.

Outbound messages related to the attribute change process are consumed in data type channels. In this case, it is only one "Attribute Change Response" channel. A Content Enricher adds a message type attribute correlating to the channel the message was placed on. This is required in order for the IMP client to properly interpret the message. After that, the message is published on the "Message Outbound Mapping" channel.

@@

To process incoming attribute change requests for profiles, a "User Profile Attribute Change Request" module is included, which consumes messages from the "Attribute Change Request" channel. Messages arriving on the "Attribute Change Request" channel were mapped from a relationship ID to a user profile ID in an earlier integration step. Depending on the use case of the Service Provider, not all attribute change requests for user profiles should be processed in the same way. Therefore, message filters are inserted which are able to distinguish possible "types" of user profiles based on the user profile ID. It would also be possible to include an additional module that is able to request user profile type information from the existing systems, separating messages on the "Attribute Change Request" channel appropriately. For example, user profiles for businesses could exist, where processing of attribute change requests requires a more thorough and manual verification by employees.

@@

Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the Service Provider. Therefore, the SP is expected to include a "Profile Attribute Change Processor" module, which decides to approve or reject the request based on the user profile ID and the shared attributes. The response is published on the "Attribute Change Response" channel and contains the user profile ID additionally to the response.

@@

If the user does not cancel the attribute change request before the OZG system accepts it, the attribute change is established. The connector is notified through a message, which eventually is processed by the "User Profile Attribute Change Message" module described earlier and published on the "Attribute Change Established" channel.

The "User Profile Attribute Sync" module consumes messages from the "Attribute Change Established" channel. Similar to the "User Profile Attribute Change Request" module, a message filter is inserted for distinguishing possible user profile types based on the user profile ID. A message translator is inserted to translate the message content to the OZG data model. This concerns especially the attributes shared as part of the "attribute change established" message.

@@

Before publishing messages on the "Message Outbound Mapping" channel, a Content Enricher adds the implicit message type of the channel as an attribute in order for the IMP client to understand it.

@@

If the user creates a user profile using their IMP identity, it is possible to replace password authentication with an authentication through the IMP client. It is also possible to use the IMP client for two-factor authentication.

To send and receive messages related to authentication, similar to previous message modules, an "Authentication Message" module is included, which maps incoming messages on the "Message Inbound Mapping" channel to the "Authentication Response" channel and outgoing messages from the "Authentication Request" channel to the "Message Outbound" channel.

@@

When the users visit the web page of the administration portal to apply for an administrative service, they will have to login. To utilize the IMP client for authentication, the web server can use a channel adapter to publish an authentication request concerning a user profile ID and a certain session ID. The adapter publishes a message on the "Authenticate" channel which contains the profile ID and a request content. Next to the session ID, the request content may also include information for presentation to the user like the current time or the IP address of the browser. Similar to the previous modules, a message translator is inserted to translate the message to a canonical data model and publish it on the "Authentication Request Message" channel.

Eventually, the IMP client sends a response as a message, which the "Authentication Message" module publishes on the "Authentication Response" channel. Similar to previous modules, the Service Provider can use a message filter to process user profile types differently. After translating the message to the OZG data model, it is published on the "Authenticate Profile Response" channel. The channel adapter of the web server receives the message and based on the session ID contained in the response content can authenticate the browser session.

@@

The messaging system and the modular approach make the integration architecture expandable and configurable for new integration scenarios.
Message mapping module and relationship mapping module enable the translation between user profile and relationship.
Onboarding template, onboarding request, and onboarding relationship module enable the definition and utilization of one or more relationship types.
Message modules enable the definition of message types.
Message processing modules enable the translation between data models.
Messaging system enables asynchronous, event-based, and direct communication between users and Service Providers.
Assigning special modules to each type of relationship and message type enables the separation of processing depending on differences in processing legitimization.

### 2021-03-26 chapters/sections/13-imp_solution_integration.tex
finished

The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection. The IMP solution described in this chapter puts the institutions in the center of the integration in order to eliminate the need for user profiles and administration portals to process personal information.

@@

Each institution has a predetermined set of administrative services it can process. For each administrative service, the institution can create a relationship template, containing the description of the service, the list of attributes required from the user necessary for processing the application and information on how the personal information will be processed:

@@

In contrast to relationship templates in the previous IMP solution, these will not have to be dynamically created but only once. The reason is that in the previous IMP solution templates had to contain personalized information like the session ID. This is not necessary in this case.

@@

When sending the relationship request, the institution directly receives it without an administration portal being involved. Based on the shared attributes, the institution can decide to either accept or reject the application request. It might for example verify whether the home address of the user is within the area that it is responsible for.

@@

After the administrative service is finished, the relationship can be terminated and the institution looses access to all shared personal information.

However, the administration portal cannot be completely replaced. It is still required by users for directing them to the correct institution based on the selected administrative service and for example their home address. Therefore users visiting any administration portal search for an administrative service and specify their home address. The administration portal is able to determine the responsible institution and forward the user to an URL provided by the institution.

@@

This IMP solution utilizes the same message types as the previous IMP solution, however for a different purpose.

@@

As a result of mapping IMP relationships to individual business processes, the user has more granular control of sharing personal information. Compared to the previous IMP solution, the user does not give general access to personal information for the purpose of creating a user profile but for individual processes. The users can better control whether they agree to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved. In case of the OZG, the user profile component did require authentication prior to sharing attributes with administration portals, but this might not be the case for all Service Providers.

Using relationships for execution of business processes eliminates the need for Service Providers to operate identity management systems. It is sufficient to integrate the identity management capabilities of the IMP system according to the IMP solution. This leaves the Service Provider with the main task of executing the business processes.

The IMP solution enables users to share personal information directly with responsible institutions, restricting access to for example administration portals. It also enables direct and secure exchange of messages.
As a result of the direct mapping of relationships to applications, users can request the modification of application content even after submission.

>>>>

The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection. The IMP solution described in this chapter puts the institutions in the center of integration to eliminate the need for user profiles and administration portals to process personal information.

@@

Each institution has a predetermined set of administrative services it can process. For each administrative service, the institution can create a relationship template, containing the description of the service, the list of attributes required from the user necessary for processing the application, and information on how the personal information will be processed:

@@

In contrast to the relationship templates in the previous IMP solution, these will not have to be dynamically created but only once. The reason is that in the previous IMP solution templates had to contain personalized information like the session ID. This is not necessary in this case.

@@

When sending the relationship request, the institution directly receives it without an administration portal being involved. Based on the shared attributes, the institution can decide to either accept or reject the application request. It might, for example, verify whether the home address of the user is within the area that it is responsible for.

@@

After the administrative service is finished, the relationship can be terminated and the institution loses access to all shared personal information.

However, the administration portal cannot be completely replaced. It is still required by users for directing them to the correct institution based on the selected administrative service and, for example, their home address. Therefore, users visiting any administration portal search for an administrative service and specify their home address. The administration portal is able to determine the responsible institution and forward the user to an URL provided by the institution.

@@

This IMP solution utilizes the same message types as the previous IMP solution, however, for a different purpose.

@@

As a result of mapping IMP relationships to individual business processes, the user has more granular control of sharing personal information. Compared to the previous IMP solution, the user does not give general access to personal information for creating a user profile but for individual processes. The users can better control whether they agree to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved. In the case of the OZG, the user profile component did require authentication prior to sharing attributes with administration portals, but this might not be the case for all Service Providers.

Using relationships for the execution of business processes eliminates the need for Service Providers to operate identity management systems. It is sufficient to integrate the identity management capabilities of the IMP system according to the IMP solution. This leaves the Service Provider with the main task of executing the business processes.

The IMP solution enables users to share personal information directly with responsible institutions, restricting access to, for example, administration portals. It also enables direct and secure exchange of messages.
As a result of the direct mapping of relationships to applications, users can request the modification of application content even after submission.
